State-space PTA

### 2023-03-16 docs/manuscript/paper.tex
explore BAT.jl

>>>>

In the case where the states are just the intrinsic pulsar frequencies, we can write the ODEs in matrix form as
\begin{equation}
	d\bar{X} = \bar{A} \bar{X} dt + \bar{N}(t) dt + \bar{\Sigma} d\bar{B}(t) 
\end{equation}
where $\bar{A} = \text{diag}(\gamma_1, \gamma_2,...)$,  $\bar{X} = \text{diag}(f_1, f_2,...)$, $\bar{N} =\text{diag}(\gamma_1[a_1+b_1t] + b_1, ...)$
and we have let $a = f_{EM}(0)$, $b = \dot{f}_{\rm EM}(0)$.
